Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report

### 2024-06-03 paper.qmd
Preparing stage 2 registered report. Moved library calls and design object update code to functions.R. Compute years_sexually_mature. Move age term to offset in poisson models.

```{r}
library(ggcorrplot)
library(tinytable)
library(patchwork)
source('functions.R')
source('pilot_analysis.R')
source('simulate.R')
source('sexspecificmodels.R')
```

@@

>>>>

```{r}
source('functions.R')
source('pilot_analysis.R')
source('simulate.R')
source('sexspecificmodels.R')
source('stage2_analysis.R')
```

@@

### Effects plots

:::{#sfig-effects}
```{r}
effects_plots(models)
```

Effects of sex-specific standardized strength on mating outcomes, by sex. Strength is centered and scaled by 2 SD, separately for each sex. Plots are based on the anthropometric control models, with control variables held at their mean values.
:::
